Click chemistry reveals an alternate mechanism for HPII catalase

### 2018-02-21 bb494/manuscript.tex
minor

First para
- reaction, relevance, structure, heme, conservation in nature

2nd para
- (talking about HPII) mechanism, channel, active site

3rd para
- catalase is FAST
- evolutionary optimizations
- why they are interesting
- what we intend to study, and why it is intersesting

4th para
- our intended experiment, wrt the dielectric constant work

@@

>>>>

First para
- reaction, relevance, structure, heme, conservation in nature
- (talking about HPII) mechanism, channel, active site

2nd para
- catalase is FAST
- evolutionary optimizations
- why they are interesting
- what we intend to study, and why it is intersesting

3rd para
- our intended experiment, wrt

@@

The study on the electric potential in the active channel \cite{electricpotential} hypothesized the existance of an orientation potential, but ___flaws_in_experiment__. We hope to more thoroughly probe this effect using genetic code expansion ____ need to figure out how this mutation should influence the active site.
